\documentclass[hidelinks, 12pt]{style} 

\usepackage[utf8]{inputenc}
\usepackage{fancyhdr} 
\pagestyle{fancy}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\graphicspath{{Images/}} 
\usepackage[backend=biber,style=phys]{biblatex}
\newtheorem{definition}{Definition}
\usepackage{tocbibind}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage[toc,title,page]{appendix}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{blindtext}
\usepackage{url}
\usepackage{epigraph}
\usepackage{tikz}
\usepackage[intoc]{nomencl}
\usepackage[makeroom]{cancel}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{chemfig}
\usetikzlibrary{quotes,arrows.meta}
\usetikzlibrary{decorations.markings}
\makenomenclature
\addbibresource{references.bib}

\usepackage{etoolbox}
\renewcommand\nomgroup[1]{%
  \item[\bfseries
  \ifstrequal{#1}{A}{Greek Letters}{}
  \ifstrequal{#1}{B}{Roman Letters}{}
]}

% This will add the units
%----------------------------------------------
\newcommand{\nomunit}[1]{%
\renewcommand{\nomentryend}{\hspace*{\fill}#1}}
%----------------------------------------------

\title{AMSIMP: An Open Source Ensemble Prediction Scheme Using Recurrent Neural Networks to Improve Numerical Weather Prediction} 

\author{Conor Casey} 
\college{Teacher: Ms. Abbott} 

\degree{Physical Sciences} 
\degreedate{SciFest@College - IT Tralee (Online)} 

\begin{document}

\pagenumbering{roman}

\maketitle

\chapter*{
\centering
    ``Although the infinitesimal calculus has been a splendid success, yet there remain problems in which it is cumbrous or unworkable. When such difficulties are encountered, it may be well to return to the manner in which they did things before the calculus was invented, postponing the passage to the limit until after the problem has been solved for a moderate number of moderately small differences”
\\[5pt]
\rightline{{\rm --- Lewis Fry Richardson}}
}

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
This report hypothesises that it is possible to create open source software implementation to simulating atmospheric dynamics, with a recurrent neural network (RNN) and ensemble prediction system (EPS) being used in combination with a physical model, that such a software implementation has a reasonable execution time to forecast length ratio, and to determine if such an implementation has a statistically significant accuracy improvement over a traditional deterministic physical model. Firstly, this report explains, and derives a series of relevant equations for simulating atmospheric dynamics on a synoptic scale.

Following this process, the software was developed and released onto the open-source platform, GitHub. To prove the hypothesis, it was determined that a series of appropriate benchmarks would be carried out in the areas of performance, and accuracy. The performance benchmark would demonstrate whether or not the software has a reasonable execution time to forecast length ratio, and the accuracy benchmark would highlight whether or not the forecasts produced by the software had a reasonable level of accuracy. Considering there is no open source software to which one can compare the software, it was determined that the software would be compared against a proprietary implementation.

In regards to performance benchmarking, the ratio between the runtime of the forecast and the fixed length of the forecast was determined. For the physical model, the ratio between the two parameters was $0.0076$; for the physical model with the RNN enabled, the ratio was $0.0799$; and for the physical model with the ensemble forecast system enabled, the ratio was $0.1147$. This correlates to a usable forecast length of 119 hours (99\%), 110 hours (92\%), and 106 hours (89\%) respectively. Hence, the forecast would be regarded as highly usable.

In regards to accuracy benchmarking, three distinct benchmarks were carried out. The purpose of the first benchmark was to determine whether the forecast produced by a given scheme of the software was more accurate than the naive forecasting model by using the mean absolute scaled error. Three parameters, geopotential height, zonal wind, and meridional wind, were consistently more accurate than the naive forecasting model across the board. The mean absolute scaled error across the entire forecasting period was $0.9399$, $0.9192$, and $0.9933$ respectively. In regards to the virtual temperature, the physical model and the physical model with the ensemble forecast system under-performed in comparison to the naive forecasting model. The physical model with the RNN enabled, however, performed better than the naive forecasting model with a mean absolute scaled error of $0.9511$. In regards to air temperature, a similar story applies, however, the physical model with the RNN in this case was unable to beat the naive forecasting model, with a mean absolute scaled error of $1.51$. In regards to relative humidity, the physical model with the RNN enabled, and the physical model with the EPS enabled performed dramatically worse than the physical model. The physical model was also unable to match the accuracy of the naive forecasting model with a mean absolute scaled error of $1.17$. That being said, the majority of the forecast schemes within the software had a higher accuracy than the naive forecasting model, hence, the software as a whole has a reasonable level of accuracy.

The purpose of the second benchmark was to determine whether a particular scheme had a statistically significant increase in accuracy over the physical model. In regards to the physical models with the RNN enabled, a statistically significant increase in accuracy was seen in two out of the six atmospheric parameters benchmarked, with a significance level of $0.1$. These were air temperature, and virtual temperature; and had a p-value of approximately $0.0543$ and $0.0115$ respectively. In regards to relative humidity, a statistically significant decrease in performance was observed. In regards to geopotential height, a RNN was not developed due to the restrictions created by the COVID-19 pandemic. Hence, a statistically significant increase or decrease in accuracy was not observed. As zonal wind, and meridional wind are determined using geopotential height, an increase or decrease in accuracy was not observed for the aforementioned parameters. Overall, using a RNN in combination with a physical model, shows significant promise. In regards to the physical models with the EPS enabled, a statistically significant increase or decrease in accuracy was not observed in any of the six atmospheric parameters benchmarked. While an increase in performance was observed across the board, except in the case of relative humidity, it was not statistically significant.

The purpose of the third benchmark was to compare the accuracy of the software's most accurate scheme against a proprietary implementation. The results shows that there is a statistically significant increase across all of the five atmospheric parameters benchmarked in favour of the forecast from the proprietary implementation. Hence, against a proprietary implementation, the software significantly under-performs. 

Hence, the hypothesis that was proposed has partially been proven, and can be accepted, as such.

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
\input{Chapters/Acknowledgements}

\tableofcontents

\listoffigures

% Nomenclatures
\mbox{}

\nomenclature[A, 01]{$\beta$}{Rossby Number 
  \nomunit{$rad \cdot s^{-1} m^{-1}$}}
\nomenclature[A, 03]{$\theta$}{Potential Temperature
  \nomunit{$K$}}
\nomenclature[A, 04]{$\lambda$}{Longitude 
  \nomunit{$^{\circ}$}}
\nomenclature[A, 05]{$\Pi$}{Exner Function
  \nomunit{$\frac{K}{K}$}}
\nomenclature[A, 06]{$\Phi$}{Geopotential Height 
  \nomunit{$m$}}
\nomenclature[A, 07]{$\phi$}{Latitude 
  \nomunit{$^{\circ}$}}
\nomenclature[A, 08]{$\varphi$}{Geopotential 
  \nomunit{$m^2 \cdot s^{-2}$}}
\nomenclature[A, 09]{$\rho$}{Density 
  \nomunit{$kg \cdot m^{-3}$}}
\nomenclature[A, 10]{$\sigma$}{Static Stability
  \nomunit{$J \cdot hPa^{-2} \cdot kg^{-1}$}}
\nomenclature[A, 11]{$\omega$}{Vertical Velocity 
  \nomunit{$Pa \cdot s^{-1}$}}
\nomenclature[A, 12]{$\Omega$}{Angular Rotation Rate of Earth
  \nomunit{$7.29246206 \cdot 10^{-5}\, rad \cdot s^{-1}$}}

\nomenclature[B, 01]{$a$}{Earth mean radius
  \nomunit{$6378100 m$}}
\nomenclature[B, 02]{$c_p$}{Specific Heat Capacity on a Constant Pressure Surface
  \nomunit{$1004, J \cdot kg^{-1} \cdot K^{-1}$}}
\nomenclature[B, 03]{$e$}{Vapour Pressure
  \nomunit{$hPa$}}
\nomenclature[B, 04]{$F$}{Coriolis Force
  \nomunit{$rad \cdot s^{-1}$}}
\nomenclature[B, 04]{$f$}{Coriolis Parameter
  \nomunit{$rad \cdot s^{-1}$}}
\nomenclature[B, 05]{$g$}{Gravitation Acceleration
  \nomunit{$m \cdot s^{-2}$}}
\nomenclature[B, 06]{$m$}{Mixing Ratio
  \nomunit{$\frac{kg}{kg}$}}
\nomenclature[B, 07]{$h$}{Pressure Thickness
  \nomunit{$m$}}
\nomenclature[B, 08]{$p$}{Pressure
  \nomunit{$hPa$}}
\nomenclature[B, 09]{$r$}{Relative Humidity
  \nomunit{$\%$}}
\nomenclature[B, 10]{$R$}{Specific Gas Constant for Dry Air
  \nomunit{$287, J \cdot kg^{-1} \cdot K^{-1}$}}
\nomenclature[B, 11]{$T$}{Temperature
  \nomunit{$K$}}
\nomenclature[B, 12]{$T_v$}{Temperature
  \nomunit{$K$}}
\nomenclature[B, 13]{$t$}{Time
  \nomunit{$s$}}
\nomenclature[B, 14]{$u$}{Zonal Wind
  \nomunit{$m \cdot s^{-1}$}}
\nomenclature[B, 15]{$v$}{Meridional Wind
  \nomunit{$m \cdot s^{-1}$}}
\nomenclature[B, 16]{$W$}{Precipitable Water
  \nomunit{$mm$}}
\nomenclature[B, 17]{$x, y$}{Horizontal Distances
  \nomunit{$m$}}
 
\printnomenclature

\chapter{Introduction} 
\pagenumbering{arabic} 
\input{Chapters/Introduction}

\chapter{Atmospheric Science}\label{2}
\input{Chapters/Atmospheric_Science.tex}

\chapter{Dynamical Core}\label{3}
\input{Chapters/Dynamical_Core.tex}

\chapter{Simulating Dynamics}\label{4}
\input{Chapters/Simulating_Dynamics.tex}

\chapter{Implementation Details}\label{5}
\input{Chapters/Implementation_Details.tex}

\chapter{Benchmarking}\label{6}
\input{Chapters/Benchmarking.tex}

\chapter{Results}\label{7}
\input{Chapters/Results.tex}

\chapter{Conclusions}\label{8}
\input{Chapters/Conclusions.tex}

\newpage

\pagenumbering{Roman}

\appendix
\renewcommand{\thesection}{\Alph{section}.\arabic{section}}
\setcounter{section}{0}
\input{Chapters/Appendices.tex}

\pagenumbering{Roman}

\printbibliography[heading = bibintoc]

\end{document}