\paragraph{Ms. Abbott} First and foremost, I would like to express my immense gratitude to my science teacher, Ms Abbott. Over the past five years, she has provided me with an unwavering amount of support and faith in any scientific endeavour I have pursued, even when I didn't have much of the latter myself. She’s always been there for me, both academically and personally. She has been a source of comfort and refuge, even in the most difficult of times. That is also not to mention the fact that she is probably the most fantastic teacher that walks the face of the planet. She would probably say I am being entirely hyperbolic, even though I wholeheartedly insist I am not. This is not a belief, it's a law of nature! Although, she does have a pathological habit of refusing to take any thanks I give her whatsoever. She is an amazing human being, even if I cannot express how grateful I am in words all the time. So, just to emphasise one last time:  THANK YOU SO, SO, SO MUCH!

\paragraph{Laura O'Sullivan}
Laura is a self-taught machine learning developer - she’s previously won prizes for exoplanet detection and cervical cancer screening research. During Patch, I collaborated with her to find the most appropriate neural network architecture, and to improve the overall performance of the existing architecture.

\paragraph{Tadhg Fitzgerald}
I have talked to a machine learning researcher, Tadhg Fitzgerald, who advised me on my machine learning implementation, as well as, providing guidance in relation to troubleshooting extensive memory issues which occurred throughout the duration of the project. His assistance was greatly appreciated.

\paragraph{Tom McCarthy and the extended Patch team}
I would like to thank the various members of the Patch Summer Accelerator Programme for their assistance in the continued development of the software. I would like to thank Tom McCarthy, founder of Patch, who supported me all through Patch with his world class guidance and counsel, Mario Kostelac, Senior Machine Learning Engineer at Intercom, who gave me outstanding advice on my machine learning implementation and troubleshooting; as well as, Andrea Vaccari, co-founder of Clearspace, who encouraged me to push myself to meet AMSIMP’s full potential. 

\paragraph{Parents} To my parents, Timmy and Frances to whom I owe everything, I would like to take the opportunity to express how grateful I am for all the support, help, guidance, feedback and love that they have provided me over these many years. I am and will be eternally grateful for this.

\paragraph{Met Éireann}
I have talked to researchers from Met Éireann, Colm Clany and Alan Hally, who advised me on the current applications of machine learning at meteorological agencies. I would like to thank them for their time commitment.

\paragraph{Irish Centre for High-End Computing}
I would like to thank the Irish Centre for High-End Computing and the people who worked therein for their continued assistance with this project, and providing computational resources which made this project possible. I am eternally grateful.

\paragraph{Scot Hosking and Rachael Furner}
I have talked to researchers from the University of Cambridge, Scot Hosking and Rachael Furner, who advised me on the current applications of machine learning at meteorological agencies, as well as, the application of machine learning in oceanography. I would like to thank them for their time commitment.

\paragraph{Nate Sauder}
I have had a conversation with Nate Sauder, who is an expert in machine learning and has worked in the meteorological industry in the past. I would like to thank them for their time commitment.

\paragraph{Mr. Healy, and Ms. Foley-Hayes}
I would like to thank Mr. Healy, and Ms. Foley-Hayes, our Principal and Vice Principal, for their support in relation to funding, incorporating various different ideas into my project, and generally providing all the assistance I needed.
