\paragraph{Ms. Abbott} First and foremost, I would like to express my immense gratitude to my science teacher, Ms Abbott. Over the past two years, she has provided me with an unwavering amount of support and faith in any scientific endeavour I have pursued, even when I didn't have much of the latter myself. She’s always been there for me, both academically and personally. She has been a source of comfort and refuge, even in the most difficult of times. That is also not to mention the fact that she is probably the most fantastic teacher that walks the face of the planet. She would probably say I am being entirely hyperbolic, even though I wholeheartedly insist I am not. This is not a belief, it's a law of nature! Although, she does have a pathological habit of refusing to take any thanks I give her whatsoever. She is an amazing human being, even if I cannot express how grateful I am in words all the time. So, just to emphasise one last time:  THANK YOU SO, SO, SO MUCH!

\paragraph{Hannah Coombs} I would like to take the opportunity to thank my dear friend, Hannah Coombs. Over these past few years, she has always been/continues to be extremely kind, and supportive to me. She has helped me gain the confidence that I was once lacking, and has made me a better person. Although she didn't provide any assistance for this particular project, I am forever indebted to her.

\paragraph{Dr. Doireann O'Kiely} I would like to thank Dr. Doireann O'Kiely for the guidance she offered for the initial phase of the project, and also providing support throughout the entirety of the project.

\paragraph{Mr. Healy, and Ms. Foley-Hayes}
I would like to thank Mr. Healy, and Ms. Foley-Hayes, our Principal and Vice Principal, for their support in relation to funding, incorporating various different ideas into my project, and generally providing all the assistance I needed.

\paragraph{Institute of Physics}
I would like to thank the the Institute of Physics for providing the physical copy of the book, `Physics of the Atmosphere' by Rodrigo Caballero.